---
title: "Simulating Plant Breeding Populations With `pbsim`"
author: "Jeff Neyhart"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


## Introduction



`r library(pbsim)`


## Making a Genome

The first step is to make a geneome object. This is essentially a `list` of class
`genome`. The object contains information such as number and length of 
chromosomes, marker positions, and genetic architecture.

Simulate a genome with three chromosomes, each with 505 markers

```{r}
n.mar  <- c(505, 505, 505)
len <- c(120, 130, 140)

genome <- sim_genome(len = len, n.mar = n.mar)

```


## Define the Genetic Model

```{r}

n.qtl <- 15
qtl.model <- matrix(NA, nrow = n.qtl, ncol = 4)

genome <- sim_gen_model(genome = genome, qtl.model = qtl.model, add.dist = "geometric")

```

## Generate a pedigree

```{r}
ped <- sim_pedigree(n.ind = 30, n.bcgen = 0, n.selfgen = 2)

```

## Simulate a family

```{r}
# First generate founders
founder_geno <- t(replicate(2, sample(x = c(0,2), size = sum(genome$n.mar), replace = T)))

fam <- sim_family(genome, ped, founder_geno)

```

## Simulate a population of many families

```{r}

# First create a crossing block






Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
